Optimal (Multiway) Spatial Joins

### 2024-05-19 msj.tex
yufei

SJ is a fundamental operation in spatial databases, which manage {\em geometric entities} such as land parcels, service areas, habitat zones, commercial districts, administrative boundaries, etc. It plays a crucial role in implementing the {\em filter-refinement mechanism}, the dominant approach for overlaying different entities in real systems. To understand why, first note that a geometric entity is typically modeled as a polygon. Determining whether two entities overlap amounts to deciding if two polygons intersect, which can be exceedingly expensive when the polygons have complex boundaries. To mitigate the issue, a spatial database stores, for each polygon $g$, its {\em minimum bounding rectangle} (MBR) defined as the smallest axis-parallel rectangle enclosing $g$. Let $G_1, G_2, ..., G_k$ be $k$ different sets of geometric entities, and $R_1, R_2, ..., R_k$ be the corresponding sets of MBRs. To compute the overlay information from $G_1, G_2, ..., G_k$, filter-refinement first executes (i) ``a filter step'', which performs an SJ to obtain $\J_k(R_1, R_2, ..., R_k)$, and (ii) a ``refinement step'', which, for each $(r_1, r_2, ..., r_k) \in \J_k(R_1, R_2, ..., R_k)$, examines if $P_1, P_2, ..., P_k$ indeed have a non-empty intersection, where $P_i$ ($i \in [1, k]$) is the entity in $G_i$ whose MBR is $r_i$.

>>>>

SJ is a fundamental operation in spatial databases (SDB), which manage {\em geometric entities} such as land parcels, service areas, habitat zones, commercial districts, administrative boundaries, etc. It plays a crucial role in implementing the {\em filter-refinement mechanism}, which is the dominant approach for overlaying different entities in an SDB. To explain this mechanism, first note that a geometric entity is typically modeled as a polygon. Determining whether two entities overlap amounts to deciding if two polygons intersect, which can be exceedingly expensive when the polygons have complex boundaries. To mitigate the issue, a spatial database stores, for each polygon $g$, its {\em minimum bounding rectangle} (MBR) defined as the smallest axis-parallel rectangle enclosing $g$; this way, each set $G$ of geometric entities spawns a set $R$ of MBRs. Consider $k$ sets of geometric entities $G_1, G_2, ..., G_k$, and the corresponding sets of MBRs $R_1, R_2, ..., R_k$. To compute the overlay information from $G_1, G_2, ..., G_k$, filter-refinement first executes (i) ``a filter step'', which performs an SJ to obtain $\J_k(R_1, R_2, ..., R_k)$, and (ii) a ``refinement step'', which, for each $(r_1, r_2, ..., r_k) \in \J_k(R_1, R_2, ..., R_k)$, examines if $P_1, P_2, ..., P_k$ indeed have a non-empty intersection, where $P_i$ ($i \in [1, k]$) is the entity in $G_i$ whose MBR is $r_i$.
